\thetitle

### 2021-01-10 paper/figures/productionsystem.tex
indep agents + n-step algorithm

\begin{tikzpicture}[queue/.style={regular polygon,regular polygon sides=4,inner sep=0.075cm},scale=0.89]

@@

  % Paths
  \path (OP.center) edge[->, bend left=10, above]
  node[xshift=0.088cm,yshift=0.05cm,align=center] {\scriptsize Order \\[-1ex] \scriptsize Release} (Q1);

  \path (M1) edge[->, bend left=10, above]                 node[xshift=-0.1cm,yshift=-0.05cm] {$\scriptstyle 1,2,3$} (Q2);
  \path (M1) edge[->, bend right=10,below]                 node[xshift=-0.1cm,yshift=-0.05cm] {$\scriptstyle 4,5,6$} (Q3);
  \path (M2) edge[->, bend left=10,above,near start ]      node {$\scriptstyle 1$}     (Q4);
  \path (M2) edge[->, bend left=10,above,near start ]      node {$\scriptstyle 2$}     (Q5);
  \path (M2) edge[->, bend left=10,above,near start ]      node[xshift=0.07cm,yshift=-0.12cm] {$\scriptstyle 3$}     (Q6);
  \path (M3) edge[->, bend right=10,above,very near start] node[xshift=0.22cm,yshift=-0.09cm] {$\scriptstyle 4$}     (Q4);
  \path (M3) edge[->, bend right=10,above,very near start]      node[yshift=-0.075cm] {$\scriptstyle 5$}     (Q5);
  \path (M3) edge[->, bend right=10,above,near start]      node {$\scriptstyle 6$}     (Q6);
  \path (M4) edge[->, bend left=10,above,near start]       node[xshift=0.1cm] {$\scriptstyle 1,4$} (\fgi{});
  \path (M5) edge[->, bend left=10,above,near start]       node[xshift=0.1cm, yshift=-0.07cm] {$\scriptstyle 2,5$} (\fgi{});
  \path (M6) edge[->, bend right=10,below,near start]      node[xshift=0.15cm,yshift=0.07cm] {$\scriptstyle 3,6$} (\fgi{});

>>>>

\begin{tikzpicture}[queue/.style={regular polygon,regular polygon sides=4,inner sep=0.075cm},scale=0.78]

@@

  % Paths
  \path (OP.center) edge[->, bend left=10, above]
  node[xshift=0.09cm,yshift=0.05cm,align=center] {\scriptsize Order \\[-1ex] \scriptsize Release} (Q1);

  \path (M1) edge[->, bend left=10, above]                 node[xshift=-0.1cm,yshift=-0.05cm] {$\scriptstyle 1,2,3$} (Q2);
  \path (M1) edge[->, bend right=10,below]                 node[xshift=-0.1cm,yshift=-0.05cm] {$\scriptstyle 4,5,6$} (Q3);
  \path (M2) edge[->, bend left=10,above,near start ]      node {$\scriptstyle 1$}     (Q4);
  \path (M2) edge[->, bend left=10,above,near start ]      node {$\scriptstyle 2$}     (Q5);
  \path (M2) edge[->, bend left=10,above,near start ]      node[xshift=0.07cm,yshift=-0.12cm] {$\scriptstyle 3$}     (Q6);
  \path (M3) edge[->, bend right=10,above,very near start] node[xshift=0.22cm,yshift=-0.09cm] {$\scriptstyle 4$}     (Q4);
  \path (M3) edge[->, bend right=10,above,very near start]      node[yshift=-0.075cm] {$\scriptstyle 5$}     (Q5);
  \path (M3) edge[->, bend right=10,above,near start]      node {$\scriptstyle 6$}     (Q6);
  \path (M4) edge[->, bend left=10,above,near start]       node[xshift=0.1cm] {$\scriptstyle 1,4$} (\fgi{});
  \path (M5) edge[->, bend left=10,above,near start]       node[xshift=0.075cm, yshift=-0.07cm] {$\scriptstyle 2,5$} (\fgi{});
  \path (M6) edge[->, bend right=10,below,near start]      node[xshift=0.15cm,yshift=0.07cm] {$\scriptstyle 3,6$} (\fgi{});

### 2021-01-10 paper/paper.tex
indep agents + n-step algorithm

\newcommand\theauthor{
  Manuel Schneckenreither% \inst{1}
  % \orcidID{0000-0002-4812-4665}
  \and Stefan Haeussler% \inst{2}
  % \orcidID{0000-0003-2589-1367}
}
\newcommand\thetitle{Average Reward Adjusted Deep Reinforcement Learning: Near-Blackwell-Optimal
  Policies for Order Release}

@@

% \authorrunning{Schneckenreither and Haeussler}
\institute{
  Department of Information Systems,
  Production and Logistics Management,
  University of Innsbruck, Austria\\
  email: \email{manuel.schneckenreither@uibk.ac.at,stefan.haeussler@uibk.ac.at}
}

@@

@@

Like \cite{MillerVeinott1969} we are considering problems that are observed in a sequence of points
in time labeled \(1,2,\ldots\) and can be modelled using a finite set of states \(\States\),
labelled \(1,2,\ldots,\size{\States}\), where the size \(\size{\States}\) is the number of elements
in \(\States\). At each point $t$ in time the system is in a state \(s_{t} \in \States\). Further,
by choosing an action $a_{t}$ of a finite set of possible actions \(A_{s}\) the system returns a
reward $r_{t} = r(s_{t}, a_{t})$ and transitions to another state \(s_{t+1} \in \States\) at time
\(t+1\) with conditional probability \(p(s_{t+1}, r_{t} \mid s_{t}, a_{t})\). That is we assume that
reaching state \(s_{t+1}\) from state \(s_{t}\) with reward \(r_{t}\) depends solely on the previous
state \(s_{t}\) and chosen action \(a_{t}\). In other words, we expect the system to possess the
Markov property \citep[p.63]{sutton1998introduction}. Reinforcement learning processes that possess
the Markov property are referred to as Markov decision processes (MDPs)
\citep[p.66]{sutton1998introduction}.
% \MS{does our system possesses the Markov property at all? :-o }

@@

\begin{algorithm}[t!]
  \begin{algorithmic}[1]
    \State{}Initialise state \(s_{0}\) and network parameters \(\netTarget, \netWorker\) randomly, set
    an exploration rate \(0 \leqslant \plearn \leqslant \pexp \leqslant 1\), exponential smoothing learning rates
    \(0 < \alpha, \gamma < 1\), and discount factors
    \(0 < \gamma_{0} < \gamma_{1} \leqslant 1\), where \(\gamma_{1} = 1\) is
    usually a good choice.
    \While{the stopping criterion is not fulfilled}
    \State{}\begin{minipage}[t]{0.9\textwidth} With probability \(\pexp\) choose a random action and
      probability \(1-\pexp\) one that fulfills
      \(\max_{a}\lexeq(\X^{\pol}_{\gamma_{1}}(s_{t},a; \netWorker{}),\X^\pol_ {\gamma_{0}}(s_{t},a; \netWorker{}))\). Let
      \(\isRandAct{t}\) indicate if the action was chosen randomly.
    \end{minipage}
    \State{}\begin{minipage}[t]{0.9\textwidth}
    Carry out action \(a_{t}\), observe reward \(r_{t}\) and resulting state \(s_{t+1}\).
    Store the experience \((s_{t}, a_{t}, \isRandAct{t}, r_{t}, s_{t+1})\) in the experience replay
    memory \(M\).
    \end{minipage}
    \If{a non-random action was chosen or \(\pexp > \plearn\)}
    \begin{align*}
      \avgrew^{\pol}  \gets (1- \alpha) \avgrew^{\pol} + \alpha [r_{t} +
      \max_{a}\X^\pol_{\gamma_1}(s_{t+1},a; \netWorker{}) - \X^\pol_{\gamma_1}(s_{t},a_{t}; \netWorker{})]
    \end{align*}
    \EndIf

    \State{}Sample random mini-batch of experiences \((s_{i}, \isRandAct{i}, a_{i}, r_{i}, s_{i})\)
    from \(M\) and do
    \begin{align*}
      y_{i,\gamma_0} & \gets r_{t} + \gamma_{0} \max_{a}
                                        \X^\pol_{\gamma_0}(s_{t+1},a; \netTarget{}) - \avgrew^{\pol} \\
      y_{i,\gamma_{1}} & \gets r_{t} + \gamma_{1} \max_{a}
                                        \X^\pol_{\gamma_1}(s_{t+1},a; \netTarget{}) - \avgrew^{\pol}
    \end{align*}
    \State{} \begin{minipage}[t]{0.9\textwidth} Update the average reward adjusted discounted
      state-values using the sum of the gradients on \({(y_{i,\cdot} -
      \X^\pol_{\cdot}(s_{t+1},a; \netWorker{}))}^{2}\) wrt. network parameters
    \(\netWorker{}\).
    \end{minipage}
    \State{} Every \(C\) steps exponential smoothly set target network:
      \(\netTarget \gets (1 - \gamma) \netTarget{} + \gamma \netWorker{}\)
    \State{} Set \(s \gets s'\), \(t \gets t+1\) and decay parameters
    \EndWhile{}
  \end{algorithmic}
  \caption{\label{alg:near}Near-Blackwell-optimal deep RL for unichain MDPs}
\end{algorithm}

@@

\subsection{Conventional Order Release Rules}

As external benchmark for comparison we use different parameterized backward infinite loading
(\BIL{}) techniques \citep{Ackerman1963}. \BIL{} uses Equation~\ref{eq:Orel} with a predetermined
and fixed lead times \(\lt_{i}\).
%
% \begin{equation*}
%   \rd_{j} = \dd_{j} - \lt_{j} \tcom
%   \label{eq:BIL}
% \end{equation*}
%
% where the release date \(RD_{j}\) of product type \(j\) is calculated by the difference of the due
% date \(DD_{j}\) and the lead time \(LT_{j}\).
Note that we set lead times for each product type and not for every order as done by
\cite{Ackerman1963}.

@@

\paragraph{Markov Decision Process.} The underlying MDP is unichain and looks as follows.
Both, state space $\mathcal{S}$ and action space $\mathcal{A}$ are discrete. Any state
$s \in \mathcal{S}$ of the \textit{state space} is composed of the following information for each
product $p$:
        %         The following information is presented to the algorithm for both Product 1 and Product 2 as follows.
\begin{itemize}

\item The currently set lead time $LT_{p} \in \{1,2,\ldots,\DDS\}$ (Recall:
  $\text{Due Date Period} - \text{Lead Time} = \text{Release Period}$). Note that we bound the
  maximum lead time with due date slack $\DDS$, which is $7$ in our setup.

\item Counters $OP_{p,d}\in \N$ for the number of orders in the order pool divided in time buckets
  with $d \in \{1,2,\ldots,\DDS \}$, which stands for the number of periods until the due date.

@@

\item Counters $Q_{i}\in \N$ standing for the number of orders for each queue $i$.

\item Counters $FGI_{p,d} \in \N$ of orders in the finished goods inventory divided in time
  buckets with $d \in \{-5,-4,-3,\ldots, \DDS \}$, which stands for the number of periods until the
  due date. Orders with a due date with more than 5 periods ago are listed in the counter
  $FGI_{-5}$.

\item Counters $S_{p,d} \in \N$ of shipped orders from the last period divided in time buckets
  with $d \in\{-5,-4,-3,\ldots, \DDS \}$, which stands for the number of periods until the due date.
  Orders with a due date with more than 5 periods ago are listed in the counter $S_{-5}$.

@@

\noindent The algorithm implicitly learns a function which maps the current state of the
production system to a release decision. In an optimal situation it does so by multiply exploring
every action for each state and assessing its economic viability.

Orders are released once the due date is within the interval $[t,t+\text{lead time}]$, whereas $t$
is the current period. Clearly, this yields bulk releases (either all or no orders with the same
due date and product type are released). % Note that we do not present past state
        %         information to the neural network.

The \textit{actions space} is composed of two independent decisions. These are the relative changes
of the lead times to the currently set lead times $LT_{p} \in \{1,2,\ldots,\DDS\}$ for each product
$p$. Recall that $p=2$.
        %
Furthermore, we restrict the action space for each state $s_{t+1}$ according to the last set lead
time $LT_{p}$ from state $s_{t}$ by restricting the change of the lead time for consecutive
periods to a maximum of 1. Thus, if $LT_{p}$ is the current lead time for product $p$ the action
space for this product is given by $\{1,2,\ldots,\DDS\} \cap \{LT_{p}-1,LT_{p},LT_{p}+1\}$. Put
differently the algorithm can increase or decrease the lead time by 1 or leave it as it is, as
long as it acts within the discrete action space given by the set $\{1,2,\ldots,\DDS\}$ for each
type of product. Thus the action space over all products is given by the full enumeration of
available actions of the individual products.

@@

\paragraph*{Reward.}
In each period the agent chooses an action which generates a reward while traversing to the next
period by simulating the production system. The rewards are the accumulated costs at the end of the
period. These costs are consist of the number of backorders, the current WIP level and the number of
orders in the inventory.
        %
        %         The costs are divided by the normalizing parameter $\eta$ (see Table~\ref{tbl:variants}) and then
        %         clipped (cut off) to the interval $[-0.5,0.5]$.

\paragraph*{Adapted Algorithm.}
The algorithm depicted above is designed as a tabular version. We have adapted it to use neural
networks for the approximation of the different kind of state-action pair value functions. This is
required due to the exponential growth of the state space. The implementation collects the observed
information for each state-action function in a replay memory and randomly selects \(128\) data
points out of a collection of \(30k\) memories in each period and trains these on the neural
network. This technique is called experience replay memory
\citep{lin1993reinforcement,mnih2015human} and ought to overcome we instabilities. Nonetheless, this
approximation results in the fact that the algorithm can be unstable or may even diverge
\citep{tsitsiklis1997analysis}. Additionally we use a target and a worker network, whereas the
target network is overwritten every \(10k\) steps by the worker network. This has been proposed by
\cite{mnih2015human} and should further stabilize the algorithm.

>>>>

\newcommand\theauthor{
  Manuel Schneckenreither\inst{1}
  % \orcidID{0000-0002-4812-4665}
  \and Stefan Haeussler\inst{1}
  % \orcidID{0000-0003-2589-1367}
  \and Juanjo Peiró\inst{2}
}
\newcommand\thetitle{Average Reward Adjusted Deep Reinforcement Learning: Near-Blackwell-Optimal
  Policies for Order Release}

@@

% \authorrunning{Schneckenreither and Haeussler}
\institute{
  Department of Information Systems, Production and Logistics Management, University of Innsbruck, Austria\\
  \email{manuel.schneckenreither@uibk.ac.at,stefan.haeussler@uibk.ac.at}
  \and
  Departament d’Estadística i Investigació Operativa, Universitat de València, Spain\\
  \email{juanjo.peiro@uv.es}
}

@@

\MS[t]{ideas: Similar Selçuk (2013) detect that a high update frequency has a negative effect and
  thus should be reduced. They conclude that the lead times ought to control the WIP level, instead
  of the due date reliability as changes are directly seen (Knollmann and Windt, 2013). For a review
  of analytical works in the context of the LTS see Bendul and Knollmann (2016).}

@@

Like \cite{MillerVeinott1969} we are considering problems that are observed in a sequence of points
in time labeled \(1,2,\ldots\) and can be modelled using a finite set of states \(\States\),
labelled \(1,2,\ldots,\size{\States}\), where the size \(\size{\States}\) is the number of elements
in \(\States\). At each point $t$ in time the system is in a state \(s_{t} \in \States\). Further,
by choosing an action $a_{t}$ of a finite set of possible actions \(A_{s}\) the system returns a
reward $r_{t} = r(s_{t}, a_{t})$ and transitions to another state \(s_{t+1} \in \States\) at time
\(t+1\) with conditional probability \(p(s_{t+1}, r_{t} \mid s_{t}, a_{t})\). That is we assume that
reaching state \(s_{t+1}\) from state \(s_{t}\) with reward \(r_{t}\) depends solely on the previous
state \(s_{t}\) and chosen action \(a_{t}\). In other words, we expect the system to possess the
Markov property \citep[p.63]{sutton1998introduction}. Reinforcement learning processes that possess
the Markov property are referred to as Markov decision processes (MDPs)
\citep[p.66]{sutton1998introduction}.

@@

\begin{algorithm}[t!]
  \begin{algorithmic}[1]
    \State{}Initialise state \(s_{0}\) and network parameters \(\netTarget, \netWorker\) randomly, set
    an exploration rate \(0 \leqslant \plearn \leqslant \pexp \leqslant 1\), exponential smoothing learning rates
    \(0 < \alpha, \gamma < 1\), and discount factors
    \(0 < \gamma_{0} < \gamma_{1} \leqslant 1\), where \(\gamma_{1} = 1\) is
    usually a good choice.
    \While{the stopping criterion is not fulfilled}
    \State{}\begin{minipage}[t]{\dimexpr\textwidth-\leftmargin-\labelsep-\labelwidth}
      With probability \(\pexp\) choose a random action and
      probability \(1-\pexp\) one that fulfills
      \(\max_{a}\lexeq(\X^{\pol}_{\gamma_{1}}(s_{t},a; \netWorker{}),\X^\pol_ {\gamma_{0}}(s_{t},a; \netWorker{}))\). Let
      \(\isRandAct{t}\) indicate if the action was chosen randomly.
    \end{minipage}
    \State{}\begin{minipage}[t]{\dimexpr\textwidth-\leftmargin-\labelsep-\labelwidth}
    Carry out action \(a_{t}\), observe reward \(r_{t}\) and resulting state \(s_{t+1}\).
    Store the experience \((s_{t}, a_{t}, \isRandAct{t}, r_{t}, s_{t+1})\) in the experience replay
    memory \(M\).
    \end{minipage}
    \If{a non-random action was chosen or \(\pexp > \plearn\)}
    \begin{align*}
      \avgrew^{\pol}  & \gets (1- \alpha) \avgrew^{\pol} + \alpha [r_{t} +
      \max_{a}\X^\pol_{\gamma_1}(s_{t+1},a; \netWorker{}) - \X^\pol_{\gamma_1}(s_{t},a_{t};
                        \netWorker{})]
      % \\ \avgrew^{\pol}  & \gets \max(\avgrew^{\pol}, \avgrew_{\min}^{\pol})\\
      % \avgrew_{\min}^{\pol} & \gets (1 - \alpha_{\min}) \avgrew_{\min}^{\pol} + \alpha_{\min} 0.975
      % \cdot \avgrew^{\pol}
    \end{align*}
    \EndIf

    \State{}Sample random mini-batch of experiences \((s_{i}, \isRandAct{i}, a_{i}, r_{i}, s_{i})\)
    from \(M\) and do
    \begin{align*}
      y_{i,\gamma_0} & \gets r_{t} + \gamma_{0} \max_{a}
                                        \X^\pol_{\gamma_0}(s_{t+1},a; \netTarget{}) - \avgrew^{\pol} \\
      y_{i,\gamma_{1}} & \gets r_{t} + \gamma_{1} \max_{a}
                                        \X^\pol_{\gamma_1}(s_{t+1},a; \netTarget{}) - \avgrew^{\pol}
    \end{align*}
    \State{} \begin{minipage}[t]{\dimexpr\textwidth-\leftmargin-\labelsep-\labelwidth} Update the average reward adjusted discounted
      state-values using the sum of the gradients on \({(y_{i,\cdot} -
      \X^\pol_{\cdot}(s_{t+1},a; \netWorker{}))}^{2}\) wrt. network parameters
    \(\netWorker{}\).
    \end{minipage}
    \State{} Every \(C\) steps exponential smoothly set target network:
      \(\netTarget \gets (1 - \gamma) \netTarget{} + \gamma \netWorker{}\)
    \State{} Set \(s \gets s'\), \(t \gets t+1\) and decay parameters
    \EndWhile{}
  \end{algorithmic}
  \caption{\label{alg:near}Near-Blackwell-optimal deep RL for unichain MDPs}
\end{algorithm}

@@

\subsection{Conventional Order Release Rule}

As external benchmark for comparison we use different parameterized backward infinite loading
(\BIL{}) techniques \citep{Ackerman1963}. \BIL{} uses Equation~\ref{eq:Orel} with a predetermined
and fixed lead times \(\lt_{i}\).
%
% \begin{equation*}
%   \rd_{j} = \dd_{j} - \lt_{j} \tcom
%   \label{eq:BIL}
% \end{equation*}
%
% where the release date \(RD_{j}\) of product type \(j\) is calculated by the difference of the due
% date \(DD_{j}\) and the lead time \(LT_{j}\).
%
% Note that we set lead times for each product group and not for every order as done by
% \cite{Ackerman1963}.

@@

\paragraph{Markov Decision Process.} The underlying MDP is unichain and looks as follows. Both,
state space $\mathcal{S}$ and action space $\mathcal{A}$ are discrete.
%
% Recall that we gproducts routed over the bottleneck machine \(M5\) are bottleneck products.
%
Any state $s \in \mathcal{S}$ of the \textit{state space} is composed of the following information
for both groups \(g\), i.e.\@ for bottleneck and non-bottleneck products:
\begin{itemize}

\item The currently set lead time $LT_{g} \in \{1,2,\ldots,\DDS\}$ (Recall:
  $\text{Due Date Period} - \text{Lead Time} = \text{Release Period}$). Note that we bound the
  maximum lead time with due date slack $\DDS$, which is $7$ in our setup.

\item Counters $OP_{g,d}\in \N$ for the number of orders in the order pool divided in time buckets
  with $d \in \{1,2,\ldots,\DDS \}$, which stands for the number of periods until the due date.

@@

\item Counters $Q_{g,i,d}\in \N$ for the number of orders in the machine and queue \(i \in
  \{M_{1}, M_{2}, \ldots , M_{6}\}\) divided in
  time buckets with $d \in \{1,2,\ldots,\DDS \}$, which stands for the number of periods until the
  due date.

\item Counters $FGI_{g,d} \in \N$ of orders in the finished goods inventory divided in time
  buckets with $d \in \{1, 2,\ldots, \DDS \}$, which stands for the number of periods until the
  due date. Orders with a due date with more than 3 periods ago are listed in the counter
  $FGI_{-3}$.

\item Counters $S_{g,d} \in \N$ of shipped orders from the last period divided in time buckets
  with $d \in\{-3,-2,\ldots, \DDS \}$, which stands for the number of periods until the due date.
  Orders with a due date with more than 3 periods ago are listed in the counter $S_{-3}$.

@@

The algorithm implicitly learns a function which maps the current state of the production
system to a lead time update and thus a release decision. In an optimal situation it does so by
multiply exploring every action for each state and assessing its economic viability.
%
Orders are released once the due date is within the interval $[t,t+\text{lead time}]$, whereas $t$
is the current period. Clearly, this yields bulk releases, meaning that either all or no orders with
the same due date and of the same product group are
released.

The \textit{action space} is composed of two decisions, the relative change of the lead times to the
currently set lead times $LT_{g} \in \{1,2,\ldots,\DDS\}$ for each product group $g$.
%
We restrict the lead time update for state $s_{t+1}$ according to the lead time $LT_{g}$ from state
$s_{t}$ by a maximum change of 1. Thus, if $LT_{g}$ is the current lead time of product group $g$
the agent can choose a lead time in $\{1,2,\ldots,\DDS\} \cap \{LT_{g}-1,LT_{g},LT_{g}+1\}$. % Put
% differently the algorithm can increase or decrease the lead time by 1 or leave it as it is, as long
% as it acts within the discrete action space given by the set $\{1,2,\ldots,\DDS\}$ for each product
% group.
A naive approach is to define one action for each combination of actions over all product groups.
Although applicable in our setup, as we only define two groups that yield \(9\) actions, it simply
does not scale.
%
\begin{figure*}[t!]
  \centering
  \input{figures/indep_agents}                      % Figure production system
  \caption{Illustration of independent agents as agent one increases the lead time}\label{fig:indep-agents}
\end{figure*}
%
Therefore, we invent and implement \textit{independent agents}, each operating on the same system
state, but choosing actions independently for the designated product group.
Figure~\ref{fig:indep-agents} illustrates the idea, where wlog. we use two agents and for simplicity
omit the reward and truncate the state to the lead times. Agent one chooses to increase the lead
time from \(3\) to \(4\). Thus, the future state, seen from agent one, depends on the probability of
agent two choosing to increase (\(\inc\)), decrease (\(\dec\)) or not change (\(\pers\)) the lead
time. Note that the Markov property the agent, that is
\(p(s_{t+1}, r_{t} \mid s_{t}, a_{t}) = p((4,\cdot), r_{t} \mid (3,3), \inc) \), is not touched by
this adaption. While for agent one the reward and future state only depends on the current state and
action taken, the corresponding probabilities for future state and reward change during the learning
process as the other agent starts to behave differently.
%
\MS[t]{independent agents, true?}This allows us to investigate the algorithms behaviour for action
solution spaces. In particular, we present the algorithm the above defined solution space not only
on the basis of product groups \(g\), but also for each product type \(p\).
That means, the state space, as well as the action space operates on a product type basis. Note that
without independent agents this is infeasible due to \(3^{6} = 729\) possible actions.

@@

\paragraph*{Reward.}
In each period the agent chooses an action which generates a reward while traversing to the next
period by simulating the production system. The rewards are the accumulated costs at the end of the
period consisting of the backorders, the WIP orders and the number of orders in the FGI. The
objective is to minimise the returned reward. Therefore, we adapt the algorithm by swapping all
maximisation functions with minimisations.

\paragraph*{Adapted Algorithm.}
Our implementation includes several optimisations, that help the algorithm in finding better
policies and stabilise the learning process. These are the above discussed independent agents that
operate on the same state, \(n\)-step learning \citep{mnih2016asynchronous}, overestimating
\(\avgrew^{\pol}\), using multiple parallel worker agents that operate on the same environment to
collect a broader range of experiences, storing experiences according to their action and uniformly
sampling over the actions to ensure each action is constantly trained to prevent catastrophic
forgetting.
%
N-step RL collects a set of consecutive experiences and

\MS[t]{explanation
  missing}

% The algorithm depicted above is designed as a tabular version. We have adapted it to use neural
% networks for the approximation of the different kind of state-action pair value functions. This is
% required due to the exponential growth of the state space. The implementation collects the observed
% information for each state-action function in a replay memory and randomly selects \(128\) data
% points out of a collection of \(30k\) memories in each period and trains these on the neural
% network. This technique is called experience replay memory
% \citep{lin1993reinforcement,mnih2015human} and ought to overcome we instabilities. Nonetheless, this
% approximation results in the fact that the algorithm can be unstable or may even diverge
% \citep{tsitsiklis1997analysis}. Additionally we use a target and a worker network, whereas the
% target network is overwritten every \(10k\) steps by the worker network. This has been proposed by
% \cite{mnih2015human} and should further stabilize the algorithm.

\MS[t]{Extensions: overestimate rho, rho minimum, Multiple Agents (shared state,  shared rho?),
  init-phase (0.5 for expSmthRewRate, always adapt rho, same rho for all agents): exp smooth reward
  as rho, replay memory actions, n-step (describe replay memory), gradient clipping }
\MS[t]{Side info: Replay memory also stores (disallowed) filtered action indices for optimisation purposes and on
episodic tasks needs to store a bool indicating an episode end. Uses Int8 for state features values.  }

\begin{algorithm}[t!]
  \begin{algorithmic}[1]
    \State{}Initialise state \(s_{0}\) and network parameters \(\netTarget, \netWorker\) randomly, set
    an exploration rate \(0 \leqslant \plearn \leqslant \pexp \leqslant 1\), exponential smoothing learning rates
    \(0 < \alpha, \gamma < 1\), and discount factors
    \(0 < \gamma_{0} < \gamma_{1} \leqslant 1\), where \(\gamma_{1} = 1\) is
    usually a good choice.
    \While{the stopping criterion is not fulfilled}
    \State{}%
    \begin{minipage}[t]{\dimexpr\textwidth-\leftmargin-\labelsep-\labelwidth}
      With probability \(\pexp\) choose a random action and
      probability \(1-\pexp\) one that fulfills
      \(\min_{a}\lexeq(\X^{\pol}_{\gamma_{1}}(s_{t},a; \netWorker{}),\X^\pol_ {\gamma_{0}}(s_{t},a;
      \netWorker{}))\). Let \(\isRandAct{t} = \mathsf{True}\) indicate that the action was chosen
      randomly
    \end{minipage}
    \State{}%
    \begin{minipage}[t]{\dimexpr\textwidth-\leftmargin-\labelsep-\labelwidth}
    Carry out action \(a_{t}\), observe reward \(r_{t}\) and resulting state \(s_{t+1}\).
    Store the experience \((s_{t}, a_{t}, \isRandAct{t}, r_{t}, s_{t+1})\) in the experience replay
    memory \(M\).
    \end{minipage}
    \If{\(t \mod{\nstep} \equiv 0\)}
    \State{Reset gradient: \(d\netWorker{} \gets 0\)}
    \State{}%
    \begin{minipage}[t]{\dimexpr\textwidth-\leftmargin-\labelsep-\labelwidth-\leftmargin+2pt}
      Sample random mini-batch of \(\nstep\) consecutive experiences from \(M\), each with
      \((s_{i}, \isRandAct{i}, a_{i}, r_{i}, s_{i})\) where \(i \in {1,2,\ldots,\nstep}\).
    \end{minipage}
    \For{each mini-batch}
    \For{each experience, starting with the latest seen experience \(\nstep\)}
    \If{experience \(\nstep\) or (\(\isRandAct{i}\) and  \(\pexp \leqslant \plearn\))}
      \State{\(\target_{\gamma0} \gets \min_{a} \X^\pol_{\gamma_0}(s_{t+1},a; \netTarget{})\)}
      \State{\(\target_{\gamma1} \gets \min_{a} \X^\pol_{\gamma_1}(s_{t+1},a; \netTarget{})\)}
    \EndIf
    \If{a non-random action was chosen or \(\pexp > \plearn\)}\\
    \hspace{2.4cm}\(\avgrew^{\pol} \gets (1- \alpha) \avgrew^{\pol} + \alpha [r_{t} +
      \min_{a}\X^\pol_{\gamma_1}(s_{t+1},a; \netWorker{}) - \X^\pol_{\gamma_1}(s_{t},a_{t};
      \netWorker{})]\)
    \EndIf
    \State{\(\target_{\gamma_0}  \gets r_{t} + \gamma_{0} \target_{\gamma_{0}} - \avgrew^{\pol}  \)}
    \State{\(\target_{\gamma_{1}}  \gets r_{t} + \gamma_{1} \target_{\gamma_{1}} - \avgrew^{\pol}\)}
    \State{\(d\netWorker{} \gets d\netWorker{} + \partial{(\target_{\gamma_{0}} - \X^\pol_{\gamma_{0}}(s_{t+1},a; \netWorker{}))}^{2} / \partial\netWorker{}\)}
    \State{\(d\netWorker{} \gets d\netWorker{} +
      \partial{(\target_{\gamma_{1}} - \X^\pol_{\gamma_{1}}(s_{t+1},a; \netWorker{}))}^{2} / \partial\netWorker{}\)}
    \EndFor{}
    \EndFor{}
    \State{Perform update of \(\netWorker{}\) using \(d\netWorker{}\)}
    \EndIf{}
    \State{Every \(C\) steps exponential smoothly set target network:
    \(\netTarget \gets (1 - \gamma) \netTarget{} + \gamma \netWorker{}\)}
    \State{} Set \(s \gets s'\), \(t \gets t+1\) and decay parameters
    \EndWhile{}
  \end{algorithmic}
  \caption{\label{alg:fin}Near-Blackwell-optimal deep RL for unichain MDPs}
\end{algorithm}
